---
title: "add_service"
editor_options:
  markdown:
    wrap: 80
---

```{r, include=FALSE, echo=FALSE, results='hide'}
source(usethis::proj_path("vignettes", "_common.R"))

path <<- "."
name <<- "repository"

file_fs <- system.file(
    "inst", "configurations", "fs.yml", 
    package = "microservices", 
    mustWork = TRUE
)

info <- config::get("add_service", file = file_fs)

microservice <- list(
    files = info$files, 
    dependencies = as.data.frame(info$dependencies)
)

microservice$files$add <- purrr::walk(
    microservice$files$add, 
    glue::glue, 
    route_name = name
)
```

Lay the infrastructure for an additional set of services. That includes adding a
unit test, adding an endpoint, and extending the entrypointy.

```{r warning=TRUE}
warning("`add_service` adds a service to pre-existing plumber microservice which you could deploy by calling `use_microservice`.")
```

## How It Works

Given a `path` to a folder and a service `name`

When `add_service(path, name)` is called

Then the function creates the following files:

```{r, code=microservice$files$add, eval=FALSE, echo=TRUE}
```

And updates the following files:

```{r, code=microservice$files$update, eval=FALSE, echo=TRUE}
```

## When to Use

In scenarios where services are thematically linked to each other. Examples for
themes that should be mounted separately:

-   'forecasting' and 'anomaly detection'
-   'user' and 'business'
