---
title: "add_plumber_service"
editor_options: 
  markdown: 
    wrap: 80
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
path <<- "."
name <<- "repository"
file_fs <- system.file("inst", "configurations", "fs.yml", package = "microservices", mustWork = TRUE)
info <- config::get("add_plumber_service", file=file_fs)
microservice <- list(files = info$files, dependencies = as.data.frame(info$dependencies))
microservice$files$add <- sapply(microservice$files$add, glue::glue, route_name = name)
```

Lay the infrastructure for an additional set of services. That includes adding a
unit test, adding an endpoint, and extending the entrypointy.

```{r warning=TRUE}
warning("`add_plumber_service` adds a service to pre-existing plumber microservice which you could deploy by calling `use_plumber_microservice`.")
```

## How It Works

Given a `path` ("`r path`") to a folder and a `name` ("`r name`")

When `add_plumber_service` is called

Then the function creates the following files:

```{r, code = microservice$files$add, eval = FALSE, echo=TRUE}
```

And updates the following files:

```{r, code = microservice$files$update, eval = FALSE, echo=TRUE}
```

## When to Use 

In scenarios where services are thematically linked to each other. Examples for
themes that should be mounted separately:

* "forecasting" and "anomaly detection"
* "user" and "business"
