---
title: "use_microservice"
editor_options: 
  markdown: 
    wrap: 80
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
file_fs <- system.file("inst", "configurations", "fs.yml", package = "microservices", mustWork = TRUE)
info <- config::get("use_microservice", file=file_fs)
microservice <- list(files = info$files, dependencies = as.data.frame(info$dependencies))
```

## How It Works

Given a `path` to a folder

When `use_microservice(path = ".")` is called

Then the function creates the following files:

```{r, code = microservice$files$add, eval = FALSE, echo=TRUE}
```

And updates the following files:

```{r, code = microservice$files$update, eval = FALSE, echo=TRUE}
```

And adds the following packages to the DESCRIPTION file:

```{r}
kable(microservice$dependencies)
```

## When to Use `plumber`

-   A Single user/machine applications.
-   Scheduled tasks. For example, you could use [AirFlow with HTTP
    Operators](https://airflow.apache.org/docs/apache-airflow-providers-http/stable/operators.html)
    to automate processes.

### `plumber` Advantages

-   Comes with familiar way to document the microservice endpoint.
-   Maturing package that comes with documentation, examples and support.

### `plumber` Disadvantages

-   Runs on a single thread. That means that parallel algorithms such as random
    forest, can only be run on one core.
-   Serves only one caller at a time.
-   Can't make inward calls for other services, That means plumber can't be
    [re-entrant](https://en.wikipedia.org/wiki/Reentrancy_(computing)). For
    example, if a microservice has three endpoints,`read_table`, `write_table`,
    and `orchestrator`, where the `orchestrator` reads a data table, transforms
    it, and writes it back, then the `orchestrator` can't make inwards calls via
    HTTP to `read_table` and `write_table`.

```{r, warning=TRUE}
warning("While `plumber` is single-threaded by nature, it is possible to perform parallel execution using the `promises` package. See links under References.")
```

## Workflow

```{r child = "vignettes/excerpts/setup-rudimentary-microservice.Rmd"}
```

## References

-   [Parallel execution in
    plumber](https://www.rstudio.com/blog/plumber-v1-1-0/#parallel-exec)
-   [`promises`
    package](https://rstudio.github.io/promises/articles/overview.html)
