---
title: "Wrinting a Microservice in R"
bibliography: []
biblio-style: apalike
link-citations: yes
editor_options: 
  markdown: 
    wrap: 80
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
```

## Why should I use Microservices?

## What is the nature of R Applications?

* Most applications are used by a small amount of users, if any
* Most applications are seldom used concurrently

## Why should I use a Microservices with R applications?

A microservice is a piece of business functionality with clear interfaces.
Implementing an Microservice around an R application, allows its integration to
platforms such as Android applications, Python applications, and commercial
off-the-shelf products (COTS) products. This is because, a typical
microservice is a process that communicate over a network throughout HTTP
requests. The caller, whether it is a Website, Android application or even
another R application, is neither aware nor care about the programming language
that powers the service.

```{r error=TRUE}
stop("Adding a Microservice increases complexity. You must have good reasons to do so.")
```

```{r message=TRUE}
message("
Good reasons to add a Microservice:

1. Scalability for non-uniform traffic
2. Error resilience
3. Separate deployments
4. Complete isolation
5. Different requirements
")
```


## Microsrvice as an R package

We can write a microservice as an [R
extension](https://cran.r-project.org/doc/manuals/r-release/R-exts.html),
specifically in a pseudo-package manner. In this mode, we take advantage of
well-documented practice and mature toolkit designated to develop R packages. To
be clear, our microservice is not an R package, rather it is built as an R
package. Writing a microservice as an R package means:

1.  We use the standard R package folder structure as a cookie cutter;
2.  We develop (write, document and test) the microservice functionally as they
    were functions of an R package.
3.  We use mature, i.e. existing and well-established, toolkit to facilitate the
    development.

While development of microservices and R packages share folder structure and
toolkit, they have a distinctly different purpose. In short, R packages "serve"
microservices, but not the converse. Rather, microservices are stand-alone
applications that *serve* a user or another system. Microservices are built
primarily be practitioners.

## Layering the Microservice Functionallity

### Seperation of Concerns

We can separate the concern of microservice functions into two:

1. Core-domain functions. These functions are not aware of the API. 
2. API functions. These functions wrap core-domain functions.

### Where does each function belong? 

Core functions belong under the `R` folder. For example, the function
`demo$class_input` (see excerpt) is part of `R/demo.R`. This function receives
any object and returns its class. It can operate without an API, e.g. calling
`demo$class_input(mtcars)` returns `data.frame`.

```{r, eval=FALSE, echo = TRUE}
demo <- new.env()

demo$class_input <- function(x = NULL){
    return(class(x))
}
```

API function, including entrypoints and endpoints, are stored outside the `R`
folder. In this demonstration they are stored under `inst/entrypoints` and
`inst/endpoints`, respectively. We discuss in entrypoints and endpoints in
length in subsequent documentations. For now, an example for an endpoint that
wraps `demo$class_input` is a nameless function located under
`inst/endpoints/plumber.R`:

```{r, eval=FALSE, echo = TRUE}
function(x = NULL){
    x <- x |> jsonlite::fromJSON(flatten = TRUE)
    demo$class_input(x)
}
```

As you can see, the nameless function knows about the existence of
`demo$class_input`, but not the converse.
