---
title: "Implementing a Microservice with Plumber"
bibliography: []
biblio-style: apalike
link-citations: yes
editor_options: 
  markdown: 
    wrap: 80
---

```{r, include = FALSE}
source(file.path(usethis::proj_get(), "vignettes",  "_common.R"))
```

## Running Microservices with **plumber** API

### The Elements of **plumber**

1.  [Foreground and Background Servers]
2.  Endpoint
3.  R Functions

### Foreground and Background Servers

This package comes with working out-of-the-box **plumber** microservice. There
are two options to spin-up the service:

1.  `entrypoints/plumber-foreground.R` runs at the foreground; and
2.  `entrypoints/plumber-background.R` runs at the background.

Originally **plumber** runs in the foreground. That means the microservice locks
down the session from running CLI commands or scripts. While this configuration
is fine during deployment, on a dedicated server, it severely impedes
development. We circumvent that hindrance by sourcing the microservice as a
local job in RStudio.

### Dissecting the plumber Entrypoint

The commands to run the demo microservice with a **plumber** API in the
foreground are:

```{r code=read_lines("entrypoints","plumber-foreground.R"), eval=FALSE, echo=TRUE}
```

1.  `plumber::Plumber$new` creates a new Plumber router object. It requires a
    path to an endpoint file, which we discuss later in this document.
2.  `plumber$setDocsCallback` by default plumber opens a browser with [OpenAPI
    Specification](https://swagger.io/specification/). OpenAPI tells the
    microservice users what URI exists, what are their parameters. In addition,
    OpenAPI allows users to fiddle around with API requests directly from
    through its GUI. While OpenAPI is highly useful, it fails when launching the
    microservice in the background. Instead, we nullify the callback function ,
    and the user can manually browse the visual documentation at
    <http://127.0.0.1:8080/__docs__/>.
3.  `plumber$run` spins up the microservice at the given `host` and `port`.

As a design choice, we store the service configuration on a yaml file and load
it to the global environment before calling `plumber$run`. The configuration
file is located in `config/r-config.yml` and its details are:

```{r code=read_lines("inst","config","r-config.yml"), eval=FALSE, echo=TRUE}
```

### Dissecting the plumber Endpoint

In the context of **plumber**, an endpoint is an R script with one or more
functions that respond to particular requests. An example for such function can
be found in the demo's endpoint at `endpoints/plumber.R`:

```{e eval = FALSE, echo = TRUE}
# Global code; gets executed at plumb() time.
pkgload::load_all()

#* Return input class
#* Return the class of the input.
#* @param x Any R data structure.
#* @get utility/class
function(x = NULL){
    x <- x %>% jsonlite::fromJSON(flatten = TRUE)
    demo$class_input(x)
}
```

In this example, there is a nameless function that will respond to GET requests
at the URN `/utility/class`. Say if the microservice URL is
`http://127.0.0.1:8080`, then the complete function address (URI) is
`http://127.0.0.1:8080/utility/class`.

This endpoint excerpt emphasis two function are beyond the standard
recommendations for **plumber**:

1.  `pkgload::load_all()` makes the functions of the microservice (in the
    excerpt case its `demo$class_input`) available to the endpoint. Originally,
    `pkgload::load_all()` is used for package development in R. Calling the
    function simulates the package under development as it were installed and
    loaded in R. In the excerpt case, `demo$class_input` lives under the "R"
    folder, and is loaded\
2.  `jsonlite::fromJSON` parses the received input into a familiar R object,
    such as a data.frame, list or some atomic data structure. Without this
    explicit call, the endpoint might misinterpret its input argument, a JSON
    string, as a character scalar.

You can find more information about **plumber** endpoints at the [package's
website](https://www.rplumber.io/articles/routing-and-input.html).

## Communicating with Microservice

### Inspecting **plumber** Behaviour

This demo include three utility URIs:

1.  `127.0.0.1:8080/utility/healthcheck` returns status 200 if server is live
    and responding.
2.  `127.0.0.1:8080/utility/class` returns the class of the object sent to the
    server. This is useful to validate a JSON string is parsed as expected on
    the microservice.
3.  `127.0.0.1:8080/utility/mirror` returns the object that was sent to the
    server. This is useful to scrutinise the returning object from the
    microservice.

### Sending and Receiving JSON

Send an object from R to the microservice with `jsonlite::toJSON`. For example,
sending mtcars to `utility/mirror`:

```{r toJSON, eval = FALSE, echo=TRUE}
input <- mtcars %>% tibble::rownames_to_column()
x <- jsonlite::toJSON(input, auto_unbox = TRUE)
url <- URLencode(paste0("http://localhost:808/utility/mirror?x=", x))
response <- httr::GET(url)
```

Parse an object returning from the microservice with `jsonlite::fromJSON`, For
example, parsing the mtcars returning from `utility/mirror`:

```{r fromJSON, eval = FALSE, echo=TRUE}
output <-
  httr::content(response) %>%
  jsonlite::fromJSON()
```
